---
title: "bill analysis"
author: "AK"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(summarytools)
library(gt)
options(scipen = 999)

working_joined <- readRDS("output/working_joined_hr1296.rds")


```

Analysis of bill sponsorship vs. not


Trump- or Hillary-won districts in 2016 (R or D)

```{r, echo=FALSE}

print(ctable(working_joined$p16winningparty,
             working_joined$stance, 
             prop = "n", headings = FALSE), method = "render")



```


GDP in district vs. national average

```{r, echo=FALSE}

print(ctable(working_joined$gdp_abovebelow_natlavg,
             working_joined$stance, 
             prop = "n", headings = FALSE), method = "render")


```


Percentage with bachelor's degree or higher vs. national average

```{r, echo=FALSE}

print(ctable(working_joined$pct.ed.college.all.abovebelow.natl,
             working_joined$stance, 
             prop = "n", headings = FALSE), method = "render")


```


Percentage of non-white population vs. national average

```{r, echo=FALSE}

print(ctable(working_joined$pct.race.nonwhite.abovebelow.natl,
             working_joined$stance, 
             prop = "n", headings = FALSE), method = "render")


```


Is more than 20% of the district's area considered rural 

```{r, echo=FALSE}

print(ctable(working_joined$pct.rural.above20,
             working_joined$stance, 
             prop = "n", headings = FALSE), method = "render")

```


Margins

```{r}

print(ctable(working_joined$margin_flag,
             working_joined$stance, 
             prop = "r", headings = FALSE), method = "render")


```






## Dems from Trump Districts only

```{r}
trump_dists_only <- working_joined %>% 
  filter(p16winningparty == "R")

```

```{r}

print(ctable(trump_dists_only$medincome.abovebelow.natl,
             trump_dists_only$stance, 
             prop = "r", headings = FALSE), method = "render")


```


```{r}

print(ctable(trump_dists_only$pct.ed.college.all.abovebelow.natl,
             trump_dists_only$stance, 
             prop = "r", headings = FALSE), method = "render")


```

```{r}

print(ctable(trump_dists_only$margin_flag,
             trump_dists_only$stance, 
             prop = "r", headings = FALSE), method = "render")


```


#### Dems on the bill from trump districts

```{r}

trump_dists_onbill <- working_joined %>% 
  filter(p16winningparty == "R",
         stance == "sponsoring")

# view(dfSummary(trump_dists_onbill))


```



#### Dems OFF the bill from trump districts

```{r}

trump_dists_offbill <- working_joined %>% 
  filter(p16winningparty == "R",
         stance == "not_sponsoring")

# view(dfSummary(trump_dists_offbill))


```
